---
title: "Star Classification"
author: "Ottia Houston"
date: "8/2/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Our goal is to be able to predict star types based on temperature, luminosity, radius, and more. We want to prove that stars follow the HR-Diagram.

Thos data set was created using several equations on 240 stars from across the internet. 

This dataset was provided by Deepraj Baidya on Kaggle.


## Prepping the data

```{r, include=FALSE}
# install libraries
library(cluster)
library(tidyverse)

#load data
starData <- read_csv("6class.csv")

#renaming
```

looking at the observations
```{r}
head(starData)
class(starData$`Star type`)
class(starData$`Star color`)
```
Based on the information we have to change the star type from a numeric to a character

Brown Dwarf -> Star Type = 0

Red Dwarf -> Star Type = 1

White Dwarf-> Star Type = 2

Main Sequence -> Star Type = 3

Supergiant -> Star Type = 4

```{r}
starData %>%
  mutate_at(vars())
```
















