---
title: "Star Classification"
author: "Ottia Houston"
date: "8/2/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Our goal is to be able to predict star types based on temperature, luminosity, radius, and more. We want to prove that stars follow the HR-Diagram.

Thos data set was created using several equations on 240 stars from across the internet. 

This dataset was provided by Deepraj Baidya on Kaggle.


## Prepping the data

```{r, include=FALSE}
# install libraries
library(cluster)
library(tidyverse)
library(factoextra)

#load data
starData <- read_csv("6class.csv")

#renaming
starData <- rename(starData, tempK = `Temperature (K)`, luminosity = `Luminosity(L/Lo)`, radius = `Radius(R/Ro)`,starType = `Star type`, starColor = `Star color`, specClass = `Spectral Class`, absMagMv = `Absolute magnitude(Mv)`)
```

looking at the observations
```{r}
head(starData)
class(starData$starType)
class(starData$starColor)
```

Based on the information we have to change the star type from a numeric to a factor.

Brown Dwarf -> Star Type = 0

Red Dwarf -> Star Type = 1

White Dwarf-> Star Type = 2

Main Sequence -> Star Type = 3

Supergiant -> Star Type = 4


But I am going to make a new dataset which gets rid of the factor variables, hehe. I chose to do this because looking at the HR model, I think that using the k-means would be the best. it seems that luminosity, temperture, and the rest is important to that. Also since I want to use a unsupervised model, I do not want a Y.
```{r}
starDataUp <- starData %>%
  select(-specClass, -starType, -starColor)
```


## Now time for the machine learning!

I think for the k, I am going to use 5 since we have six star types.
```{r}
set.seed(1) # for reproduction

m = 6 # the means clustering that I would like
km = kmeans(starDataUp, centers = m)
```

#looking at the data

```{r}
km
```

Now to look at it visually

```{r}
fviz_cluster(km, data = starDataUp, geom = "point", stand = FALSE)
```











